---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# canlang

<!-- badges: start -->
<!-- badges: end -->

The goal of canlang is to easily share language data collected in the 2016 Canadian census.

## Installation

You can install the development version from [GitHub](https://github.com/) with:

``` r
# install.packages("devtools")
devtools::install_github("ttimbers/canlang")
```
## Example

The data set `mother_tongue` lists the counts of how many Canadians report each language as their mother tongue. This data was recorded in the 2016 Census:

```{r example-1}
library(canlang)
head(mother_tongue)
```

The data set `lang_spoken_at_home` lists the counts of how many Canadians report each language as the language they speak most often at home. This data was recorded in the 2016 Census:

```{r example-2}
library(canlang)
head(lang_spoken_at_home)
```
